Haplotype Inference via Boolean Satisfiability and Integer Linear Programming

### 2020-12-01 presentation.tex
minor fixes

\title[]{Comparing SAT and ILP for Haplotype Inference} % The short title appears at the bottom of every slide, the full title is only on the title page

@@

\begin{frame}
\begin{itemize}
\item Given a genotype, what are the haplotypes resolving into this genotype?
\item Genotype 0021201 can be resolved into different pairs of haplotypes
\begin{itemize}
\item $\begin{matrix}
0001001  \\\hline
0011101 
\end{matrix}$
\item $\begin{matrix}
0011001 \\\hline
0001101 
\end{matrix}$
\end{itemize}
\item Which one is the correct pair of haplotypes?
\item Pure parsimony
\item Experimentally validated to give relatively accurate results
\end{itemize}
\end{frame}

@@

\begin{frame}
\frametitle{RTIP}
\begin{itemize}
\item Formulated by Gusfield~\cite{DBLP:conf/cpm/Gusfield03}
\item Idea: unfold potential haplotype pairs and use ILP to choose a minimum-size set to explain genotypes
\item $\mathcal{G} = \{g_i\}$ set of $n$ genotypes of length $m$
\item Assign binary variable $x_i$ for each potential haplotype
\item Haplotype $h_i$ is used iff $x_i = 1$
\item Binary variable $y_{i,j}$ for each haplotype pair $p_j$
\item $y_{i,j} = 1$ iff haplotype pair $p_j$ is used to explain genotype $g_i$ 
\item Goal: Minimize $\displaystyle \sum_i x_i$
\end{itemize}
\end{frame}

>>>>

\title[]{Haplotype Inference via Boolean Satisfiability and Integer Linear Programming} % The short title appears at the bottom of every slide, the full title is only on the title page

@@

\begin{frame}
\begin{itemize}
\item Given a genotype, what are the haplotypes resolving into this genotype?
\item Genotype 0021201 can be resolved into different pairs of haplotypes
\begin{itemize}
\item $\begin{matrix}
0001001  \\\hline
0011101 
\end{matrix}$
\item $\begin{matrix}
0011001 \\\hline
0001101 
\end{matrix}$
\end{itemize}
\item Which one is the correct pair of haplotypes?
\item Pure parsimony
\item Experimentally validated to give relatively accurate results~\cite{DBLP:journals/bioinformatics/WangX03a}
\end{itemize}
\end{frame}

@@

\begin{frame}
\frametitle{RTIP}
\begin{itemize}
\item Formulated by Gusfield~\cite{DBLP:conf/cpm/Gusfield03}
\item Idea: unfold potential haplotype pairs and use ILP to choose a minimum-size set to explain genotypes
\item $\mathcal{G} = \{g_i\}$ set of $n$ genotypes of length $m$
\item Assign binary variable $x_i$ for each potential haplotype
\item Haplotype $h_i$ is used iff $x_i = 1$
\item Binary variable $y_{i,j}$ for each haplotype pair $p_j$ of $g_i$
\item $y_{i,j} = 1$ iff haplotype pair $p_j$ is used to explain genotype $g_i$ 
\item Goal: Minimize $\displaystyle \sum_i x_i$
\end{itemize}
\end{frame}
